% Thesis Acknowledgements ------------------------------------------------

\begin{acknowledgements}
    This work, and my graduate studies as a whole, was made possible
    by the support of numerous friends, colleagues, advisors, and food
    vendors scattered throughout Philadelphia.
    I'd like to thank first and foremost Josh Klein.
    He's been a fun person to work with, and a ceaseless fountain
    of knowledge and wisdom.
    I can only hope that in my future endeavors I can approach problems with
    the level of both enthusiasm and patience that Josh manages.

    I owe a great deal to all the grad-students and postdocs I've
    worked with at Penn.
    Thank you for all the 12-hour car rides, questions and answers,
    lunches, trips underground, meandering conversations,
    and occasional games of poker.
    I'd like to give particular thanks Andy and Richie. When I started at Penn
    I didn't know very much at all about neutrinos and the
    ins and outs of experimental particle physics.
    Their help provided me valuable footholds from which I could
    work my way towards understanding.
    I owe Tanner a great deal as well,
    if for no other reason than because he helped replace the feed-resistors
    for like five-hundred PMTs.
    Tanner is always fun to hangout with in Sudbury, he's a sage of Heroes-III, and
    person who knows a lot about stuff that I don't know much about.
    I also owe special thanks to Ian. He and I shared the  task of getting
    TUBii up and running.
    It was a difficult process because we were both at least a bit in over our
    heads, but over the course of probably about a thousand emails he and I
    got things running, mostly.
%    And finally I'll give a big non-specific roundup, thank you to David(s), Tony, Meng, Jon,
%    Logan, Nuno, Shannon, Jorge, Stan, Sean, 


    I'd like to thank the instrumentation group here at Penn.
    Rick and Godwin are the embodiements of the phrase
    institutional knowledge.
    They were another source from which I was able to gain
    understanding about how to move from problem A to problem B in my electronics
    work.

     


\end{acknowledgements}

% ------------------------------------------------------------------------


